Competing Bandits: \\ The Perils of Exploration under Competition

### 2018-11-06 paper/content/model.tex
Minor edit.

\xhdr{Consistency.}
While we experiments with various MAB instances and parameter settings, in the main paper we only report plots for selected, representative experiments. Additional plots can be found in the supplement. Unless noted otherwise, our findings are based on and consistent with all these plots.

>>>>

\asedit{\xhdr{Consistency.}}
While we experiments with various MAB instances and parameter settings, in the main paper we only report plots for selected, representative experiments. Additional plots will be published in the full version. Unless noted otherwise, our findings are based on and consistent with all these plots.
